Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-11-09 tex/scam/coverletter.tex
edit

We would like to submit the manuscript ``Faithful variable selection
for high dimensional convex regression'' for review and possible
publication in {\it The Annals of Statistics}.  This paper develops a
new procedure based on additive models for variable selection in high
dimensional convex regression, shows that the procedure yields no
false negatives in the population setting, and gives a finite sample
statistical analysis.

>>>>

We would like to submit the manuscript ``Faithful variable screening
for high-dimensional convex regression'' for review and possible
publication in {\it The Annals of Statistics}.  This paper develops a
new procedure based on additive models for variable selection in high
dimensional convex regression, shows that the procedure yields no
false negatives in the population setting, and gives a finite sample
statistical analysis.
